---
title: "Very Advanced Polyphasic Algorithmic Programming"
author: "Gurpreet Singh"
date: '`r Sys.Date()`'
output:
  ioslides_presentation:
    widescreen: true
    df_print: paged
---

---
# Prof wants these things:
# Explain Problem
# Explain dataset with example of single entry
# Explain potential datascience methods
# Ability to answer questions about data
# Keep it under 10 mins
# 5% of mark
---

## Problem

its some wild shit ya kno. mans  be out here coding and shit
Subject matter
What is {Term Definition}
Programming technologies progress so quickly that textbooks don't work anymore

## Project Plan

Create a way for code to be analyzed and evaluated correctly
 
## Significance

This can help teachers, interviews, etc
Past work

# Avaliable data
time for some R fun

## Questions Data {.smaller}

```{r}
questions <- read.csv("data/questions.csv")
str(questions)
head(questions, 2)
```

## Questions Data {.smaller}
```{r}
library(forcats)
library(ggplot2)
questions$level = fct_infreq(questions$level)
qplot(level, fill = level, data = questions, geom = "bar")
```

## Solution Data {.smaller}

```{r}
solutions <- read.csv("data/solutions.csv")
str(solutions)
head(solutions, 2)
```

## Solution Data {.smaller}

```{r}
runtimeErrors <- c("runtime error(SIGABRT)", "runtime error(SIGFPE)", "runtime error(OTHER)", "runtime error(NZEC)", "runtime error(SIGXFSZ)", "runtime error(SIGSEGV)", "")
solutions$Status <- solutions$Status %>% fct_collapse("runtime errors" = runtimeErrors)
solutions$Status = fct_infreq(solutions$Status)
qplot(Status, fill = Status, data = solutions, geom = "bar") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Code Data {.smaller}

```{r}
code <- read.csv("data/first.csv")
str(code)
head(code, 1)
```

# Plan for Analysis

## Feature creation
Combining data
Processing the code into a statistic
Processing the question into a statistic

## Plan for Visualization
Scatterplot
Silhouette plot (for clustering too many dimensions)
Reduce dimensions using KSNE
Scatterplot to test efficiency of medol

# Current Issues
idk what im doing?

## New York City Flights 2013 {.smaller}

